RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-28 discussion.tex
yes

{\bf Security.}
% We sprinkle the security dust on at the end!
Our environment assumes a high degree of trust between users.
Access control for information security is delegated to the host
operating system and web server. In practice, most operating
systems and web servers rely either on coarse permission models,
which tend to be ineffective, or on detailed access control
lists, which tend to be cumbersome and complicated. 
Information security in RCloud should be re-examined, but more
sophisticated approaches such as information flow analysis are
still an active research area, and many subtle problems remain
\cite{Moore:2011:SAF}. We are hopeful that having a richer
environment for collaboration and information sharing will encourage
practical applications for new approaches to information security
in visual analytics.

>>>>

{\bf Security.}
It is essential to provide security in an environment that encourages
collaboration and data publishing.  RCloud uses an object capability model
\cite{Miller:2006:RCT}
recently added to the Rserve protocol \cite{Urbanek:2003:AFW}
that prevents unauthenticated clients from making
unauthorized calls to the RCloud runtime environment.

Our back-end environment assumes a high degree of trust between users.
Access control for information security is delegated to the host
operating system and web server. In practice, most operating
systems and web servers rely either on coarse permission models,
which tend to be ineffective, or on detailed access control
lists, which tend to be cumbersome. 
Information security in RCloud should be re-examined, but more
sophisticated approaches such as information flow analysis are
still an active research area, and many subtle problems remain
\cite{Moore:2011:SAF}. We are hopeful that having a richer
environment for collaboration and information sharing will encourage
practical applications for new approaches to information security
in visual analytics.
